---
title: "Symbiont shuffling analysis"
author: "Ross Cunning"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)

library(lsmeans)
library(effects)
library(scales)
library(plotly)
library(tidyverse)
```

### Load symbiont shuffling analysis from GitHub
```{r}
# Loads saved workspace from full analysis of symshuff-3c project
githubURL <- "https://github.com/jrcunning/symshuff-3c/raw/master/analysis/analysis.RData"
load(url(githubURL))
```

### Get proportion symbionts lost for each coral species in each treatment
```{r symbiont_loss}
symloss <- bind_rows(SsOf, Mc) %>%
  select(Species, BleachLvl, PropD.init, Total.init, Total.bleach) %>%
  glm(log(Total.bleach/Total.init) ~ PropD.init + Species*BleachLvl, data=., family=gaussian) %>%
  lsmeans(object=., specs=c("Species", "BleachLvl")) %>% summary(.) %>%
  mutate(pct.loss = 1 - exp(lsmean)) %>%
  select(Species, BleachLvl, pct.loss)

symloss
```

### Get photochemical advantage of D under heat stress in each coral species 
```{r photochemical_advantage}
ADH <- unique(df[,c("Species", "ADH")])

ADH
```

### Calculate integrated shuffling response for each coral in each treatment
```{r shuffling}
shuffle <- bind_rows(SsOf, Mc) %>%
  select(Species, BleachLvl, RecovTemp, PropD.init, PropD.recov) %>%
  mutate(RecovTemp = factor(RecovTemp)) %>%
  glm(PropD.recov ~ PropD.init + Species*BleachLvl*RecovTemp, data=., family=quasibinomial) %>%
  lsmeans(., specs=c("PropD.init", "Species", "BleachLvl", "RecovTemp"), 
          at = list(PropD.init = seq(0, 1, 0.01)), type = "response") %>% summary() %>% 
  group_by(Species, BleachLvl, RecovTemp) %>%
  summarise(shuffle = (mean(prob)-0.5)/0.5)

shuffle
```

### Model shuffling response with symbiont loss, photochemical advantage of D, and recovery temperature as predictors
```{r}
predictors <- full_join(symloss, ADH)

mod <- full_join(predictors, shuffle) %>%
  mutate(shuffle.scaled = scales::rescale(shuffle, from=c(-1, 1), to=c(0, 1))) %>%
  glm(shuffle.scaled ~ pct.loss * ADH * RecovTemp, family=quasibinomial, data=.)

modres <- anova(mod, test="F")
pseudoR2 <- with(summary(mod), 1 - deviance / null.deviance)
pseudoR2

pred <- mod %>%
  lsmeans(., specs=c("pct.loss", "ADH", "RecovTemp"),
          at = list(pct.loss = seq(0.5, 1, len = 10), 
                    ADH = seq(0, 0.15, len= 10),
                    RecovTemp = factor(c(24, 29))),
          type = "response") %>% summary() %>%
  mutate(shuffle = scales::rescale(prob, from=c(0,1), to=c(-1,1)))

# Generate matrices for plotting
dat24 <- pred %>%
  filter(RecovTemp==24) %>%
  select(pct.loss, ADH, shuffle) %>%
  spread(pct.loss, shuffle) %>%
  remove_rownames() %>% 
  column_to_rownames(var = "ADH")

dat29 <- pred %>%
  filter(RecovTemp==29) %>%
  select(pct.loss, ADH, shuffle) %>%
  spread(pct.loss, shuffle) %>%
  remove_rownames() %>% 
  column_to_rownames(var = "ADH")
         

# plot 2d surface plots for each recovtemp separately

p <- plot_ly() %>%
  add_contour(x=seq(0.5, 1, len=10), y=seq(0, 0.15, len=10), z=as.matrix(dat24), colorscale="Jet") %>%
  layout(xaxis=list(title="Pct bleaching"),
         yaxis=list(title="Advantage D"))
p

p <- plot_ly() %>%
  add_contour(x=seq(0.5, 1, len=10), y=seq(0, 0.15, len=10), z=as.matrix(dat29), colorscale="Jet") %>%
  layout(xaxis=list(title="Pct bleaching"),
         yaxis=list(title="Advantage D"))
p

# plot 3d surface plots for both recovtemps together
m <- list(l=0, r=0, b=0, t=0, pad=0)
zero <- matrix(rep(0, 100), ncol=10, nrow=10)
p <- plot_ly() %>% 
  add_surface(x=seq(0.5, 1, len=10), y=seq(0, 0.15, len=10), z=as.matrix(dat24), 
              cmin=-1, cmax=1, colorscale="Jet", opacity=0.7, showscale=FALSE) %>%
  add_surface(x=seq(0.5, 1, len=10), y=seq(0, 0.15, len=10), z=as.matrix(dat29), 
              cmin=-1, cmax=1, colorscale="Jet", opacity=0.7, showscale=FALSE) %>%
  #colorbar(len=0.5, opacity=0.7) %>%
  layout(scene=list(aspectmode='manual', 
                    aspectratio=list(x=0.85, y=0.85, z=0.85),
                    xaxis=list(title="", tickvals=c(0.4, 0.6, 0.8, 1)),
                    yaxis=list(title="", tickvals=c(0, 0.05, 0.1, 0.15), 
                               ticktext=c("0", "0.05", "0.1", "")),
                    zaxis=list(title="", range=c(-1,1), zeroline=TRUE),
                    camera=list(eye=list(x=-1.4,y=-1.5,z=0.43))),
         margin = m)
p

```


```{r}
### SAVE PLOTLY IMAGE USING ACCOUNT
#Sys.setenv("plotly_username"="jrcunning")
#Sys.setenv("plotly_api_key"="a6BKmUYVTYhBNWxlxFwA")

plotly_IMAGE(p, format = "png", width=600, height=500, out_file = "figures/fig3_plotly.png")
```


